---
title: "Combined Data"
output: html_document
date: "2024-07-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE)
```

```{r}
# install.packages("devtools")
devtools::install_github("bio-oracle/biooracler")
library(biooracler)
library(tidyverse)
library(stars)
```

2050 ssp245
```{r}
dataset_id = "thetao_ssp245_2020_2100_depthsurf"

time = c('2050-01-01T00:00:00Z', '2050-01-01T00:00:00Z')

latitude = c(-58, 78) 
longitude = c(-179.975, -74) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "thetao_mean"
              
# fill in here
temp_mean2 <- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)

dataset_id = "mlotst_ssp245_2020_2100_depthsurf"

time = c('2050-01-01T00:00:00Z', '2050-01-01T00:00:00Z')

latitude = c(-58, 78) 
longitude = c(-179.75, -76.9844) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "mlotst_mean"
              
# fill in here
mld_mean2 <- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)

dataset_id = "chl_ssp245_2020_2100_depthsurf"

time = c('2050-01-01T00:00:00Z', '2050-01-01T00:00:00Z')

latitude = c(0, 58.21155) 
longitude = c(-179.975, -76.9844) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "chl_mean"
              
# fill in here
chl_mean2 <- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)
```

2050 ssp 460
```{r}
dataset_id = "thetao_ssp460_2020_2100_depthsurf"

time = c('2050-01-01T00:00:00Z', '2050-01-01T00:00:00Z')

latitude = c(-58, 78) 
longitude = c(-179.975, -74) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "thetao_mean"
              
# fill in here
temp_mean4 <- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)

dataset_id = "mlotst_ssp460_2020_2100_depthsurf"

time = c('2050-01-01T00:00:00Z', '2050-01-01T00:00:00Z')

latitude = c(-58, 78) 
longitude = c(-179.75, -76.9844) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "mlotst_mean"
              
# fill in here
mld_mean4 <- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)

dataset_id = "chl_ssp460_2020_2100_depthsurf"

time = c('2050-01-01T00:00:00Z', '2050-01-01T00:00:00Z')

latitude = c(0, 58.21155) 
longitude = c(-179.975, -76.9844) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "chl_mean"
              
# fill in here
chl_mean4 <- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)
```


2090 ssp2 (45)
```{r}
dataset_id = "thetao_ssp245_2020_2100_depthsurf"

time = c('2090-01-01T00:00:00Z', '2090-01-01T00:00:00Z')

latitude = c(-58, 78) 
longitude = c(-179.975, -74) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "thetao_mean"
              
# fill in here
temp_2090_ssp2 <- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)

dataset_id = "mlotst_ssp245_2020_2100_depthsurf"

time = c('2090-01-01T00:00:00Z', '2090-01-01T00:00:00Z')

latitude = c(-58, 78) 
longitude = c(-179.75, -76.9844) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "mlotst_mean"
              
# fill in here
mld_2090_ssp2 <- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)

dataset_id = "chl_ssp245_2020_2100_depthsurf"

time = c('2090-01-01T00:00:00Z', '2090-01-01T00:00:00Z')

latitude = c(0, 58.21155) 
longitude = c(-179.975, -76.9844) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "chl_mean"
              
# fill in here
chl_2090_ssp2 <- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)
```


2090 ssp 460
```{r}
dataset_id = "thetao_ssp460_2020_2100_depthsurf"

time = c('2090-01-01T00:00:00Z', '2090-01-01T00:00:00Z')

latitude = c(-58, 78) 
longitude = c(-179.975, -74) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "thetao_mean"
              
# fill in here
temp_2090_ssp4<- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)

dataset_id = "mlotst_ssp460_2020_2100_depthsurf"

time = c('2090-01-01T00:00:00Z', '2090-01-01T00:00:00Z')

latitude = c(-58, 78) 
longitude = c(-179.75, -76.9844) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "mlotst_mean"
              
# fill in here
mld_2090_ssp4 <- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)

dataset_id = "chl_ssp460_2020_2100_depthsurf"

time = c('2090-01-01T00:00:00Z', '2090-01-01T00:00:00Z')

latitude = c(0, 58.21155) 
longitude = c(-179.975, -76.9844) 

constraints = list(time, latitude, longitude)
names(constraints) = c("time", "latitude", "longitude")

variables = "chl_mean"
              
# fill in here
chl_2090_ssp4 <- download_layers(dataset_id = dataset_id, variables = variables, constraints = constraints)